CamIO data analysis

### 2020-06-10 R/01-visualizations.Rmd
Update analysis & figs

```{r}
fig <- data.long %>% 
  group_by(mode) %>% 
  mutate(med = median(time)) %>% 
  ungroup() %>%
  ggplot(aes(x=time, fill=mode, color=mode)) +
  geom_histogram(binwidth=12, fill="white", boundary = 1) + #aes(y=..density..)
  geom_density(alpha=0.6, adjust=6) + 
  theme(legend.position = "none") +
  labs(x = "Time to find hotspot", y="Count") +
  facet_wrap(. ~ mode) +
  geom_vline(aes(xintercept=med, group=mode, color=mode), linetype="dashed", size=1) +
  geom_text(aes(x=med - 10, label=med, y=-1.5))

>>>>

```{r}
fig <- data.long %>% 
  group_by(mode) %>% 
  mutate(med = median(time)) %>% 
  ungroup() %>%
  ggplot(aes(x=time, fill=mode, color=mode)) +
  geom_histogram(binwidth=15, fill="white", boundary = 1) + #aes(y=..density..)
  geom_density(alpha=0.6, adjust=6) + 
  theme(legend.position = "none") +
  #theme_bw() +
  labs(x = "Time to find hotspot", y="Count") +
  coord_fixed(ratio=5) +
  facet_wrap(. ~ mode) +
  geom_vline(aes(xintercept=med, group=mode, color=mode), linetype="dashed", size=1) +
  geom_text(aes(x=med - 10, label=med, y=-1.5))

### 2020-06-10 R/02-analysis.Rmd
Update analysis & figs

```{r}
wilcoxon.res <- wilcox.test(data.wide.GN$N, data.wide.GN$G, alternative="two.sided", paired=TRUE, conf.int=TRUE)

summary.wilcoxon <- wilcoxon.res %>% tidy

DT::datatable(
  summary.wilcoxon,
  class = 'cell-border stripe compact',
  options = list(autoWidth = TRUE),
  caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: center;',
    glue('Fig {tc<-tc+1}: Signed-Rank Wilcoxon Test summary')
  )
) %>% formatRound(1:5, 2)
```

@@

```{r}
glmm1 <- lmer(time ~mode + (1|id/mode), data=data.long.time2)
glmm1
```

>>>>

```{r}
wilcoxon.res <- wilcox.test(data.wide.GN$N, data.wide.GN$G, paired=TRUE, conf.int=TRUE, correct = FALSE)

wilcoxonZ(
  data.wide.GN$N,
  data.wide.GN$G,
  mu = 0,
  paired = TRUE,
  exact = FALSE,
  correct = FALSE,
  digits = 3
)

wilcoxon.res %>% tidy
```
```{r}
median(data.wide.GN$G)
median(data.wide.GN$N)
```

@@

```{r}
glmm1 <- lmer(time ~mode + (1|subject), data=data.long.time2)
glmm1
```

### 2020-06-10 R/Index.Rmd
Update analysis & figs

if (!require(knitr)) install.packages("knitr")
if (!require(pacman)) install.packages("pacman")
pkg_list <- c("tidyverse", "glue", "broom", "magrittr", "prettydoc", "DT", "reshape2", "plotly", "moments", "emmeans", "gtsummary", "lmtest", "table1", "rstatix", "lme4", "ggeffects", "conflicted", "forecast", "Rmisc", "gridExtra", "kableExtra", "magick", "webshot")

>>>>

if (!require(knitr)) install.packages("knitr")
if (!require(pacman)) install.packages("pacman")
pkg_list <- c("tidyverse", "glue", "broom", "magrittr", "prettydoc", "DT", "reshape2", "plotly", "moments", "emmeans", "gtsummary", "lmtest", "table1", "rstatix", "lme4", "ggeffects", "conflicted", "forecast", "Rmisc", "gridExtra", "kableExtra", "rcompanion")
